European or American? A re-examination of the transatlantic influence over the IMF

### 2025-08-07 manuscript/manuscript.qmd
rephrase colonial results interpretation

Contrary to the colonial preference hypothesis, the interaction terms (`EUP Influence` $\times$ `African recipient`) are statistically insignificant in most specifications, and when significant, they are negative — indicating that African recipients, if anything, benefit less from European influence than non-African borrowers with comparable ties. Likewise, the `African recipient` variable itself is not associated with systematically more favourable lending outcomes, and in some models is linked to less favourable terms.

>>>>

Contrary to the colonial preference hypothesis, the interaction terms (`EUP Influence` $\times$ `African recipient`) are statistically insignificant in most specifications, and when significant (as in the participation rate model), they are *negative* — indicating that ties with Western European powers, if anything, bring fewer benefits to African recipients than to non-African borrowers. Similarly, the `African recipient` variable itself is not consistently associated with more favourable IMF lending outcomes; in fact, in some models (participation rate and conditionality), it is significantly correlated with *less* favourable terms. Taken together, these results suggest that African recipients do not benefit disproportionately from their historical or post-colonial relationships with European powers—and may, on average, receive less favourable treatment than non-African countries with comparable political ties and economic profiles.
